\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-12 papers/jss/article.Rnw
mostly spelling
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@762 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\title{RProtoBuf: Efficient Cross-Language Data Serialization in R}
\author{by Dirk Eddelbuettel and Murray Stokely}

@@

\emph{Comma-separated values} (CSV) files can be read and written by many
applications and so are often used for exporting tabular data.  However, CSV
files have a number of disadvantages, such as a limitation of exporting only
tabular datasets, lack of type-safety, inefficient text representation and
parsing, possibly limited precision and ambiguities in the format involving
special characters.  \emph{JavaScript Object Notation} (JSON) is another
widely-supported format used mostly on the web that removes many of these
disadvantages, but it too suffers from being too slow to parse and also does
not provide strong typing between integers and floating point.  Because the
schema information is not kept separately, multiple JSON messages of the same
type needlessly duplicate the field names with each message.  Lastly,
\emph{Extensible Markup Language} (XML) is a well-established and widely-supported
protocol with the ability to define just about any arbitrarily complex
schema. However, it pays for this complexity with comparatively large and
verbose messages, and added complexities at the parsing side (which are
somewhat metigated by the availability of mature libraries and
parsers).

@@

Once the data serialization needs of an application become complex
enough, developers typically benefit from the use of an
\emph{interface description language}, or \emph{IDL}.  IDLs like
Protocol Buffers \citep{protobuf}, Apache Thrift, and Apache Avro provide a compact
well-documented schema for cross-langauge data structures and
efficient binary interchange formats.  The schema can be used to
generate model classes for statically-typed programming languages such
as C++ and Java, or can be used with reflection for dynamically-typed
programming languages.  Since the schema is provided separately from
the encoded data, the data can be efficiently encoded to minimize
storage costs of the stored data when compared with simple
``schema-less'' binary interchange formats.
Many sources compare data serialization formats and show Protocol
Buffers very favorably to the alternatives; see
\citet{Sumaray:2012:CDS:2184751.2184810} for one such comparison.

@@

But when the values are specified as character strings, RProtoBuf
will automatically coerse them into a true 64-bit integer types 
before storing them in the Protocol Buffer message:

@@

There are \Sexpr{n} standard data sets included in the base-r \pkg{datasets}
package. These datasets include data frames, matices, timeseries, tables lists,
and some more exotic data classes. The \texttt{can\_serialize\_pb} method can be 
used to determine which of those can fully be converted to the \textt{rexp.proto}
Protocol Buffer representation:

>>>>

\title{RProtoBuf: Efficient Cross-Language Data Serialization in R}
\author{by Dirk Eddelbuettel, Murray Stokely and Jeroen Ooms}

@@

\emph{Comma-separated values} (CSV) files can be read and written by many
applications and so are often used for exporting tabular data.  However, CSV
files have a number of disadvantages, such as a limitation of exporting only
tabular datasets, lack of type-safety, inefficient text representation and
parsing, possibly limited precision and ambiguities in the format involving
special characters.  \emph{JavaScript Object Notation} (JSON) is another
widely-supported format used mostly on the web that removes many of these
disadvantages, but it too suffers from being too slow to parse and also does
not provide strong typing between integers and floating point.  Because the
schema information is not kept separately, multiple JSON messages of the same
type needlessly duplicate the field names with each message.  Lastly,
\emph{Extensible Markup Language} (XML) is a well-established and widely-supported
protocol with the ability to define just about any arbitrarily complex
schema. However, it pays for this complexity with comparatively large and
verbose messages, and added complexities at the parsing side (which are
somewhat mitigated by the availability of mature libraries and
parsers).

@@

Once the data serialization needs of an application become complex
enough, developers typically benefit from the use of an
\emph{interface description language}, or \emph{IDL}.  IDLs like
Protocol Buffers \citep{protobuf}, Apache Thrift, and Apache Avro provide a compact
well-documented schema for cross-language data structures and
efficient binary interchange formats.  The schema can be used to
generate model classes for statically-typed programming languages such
as C++ and Java, or can be used with reflection for dynamically-typed
programming languages.  Since the schema is provided separately from
the encoded data, the data can be efficiently encoded to minimize
storage costs of the stored data when compared with simple
``schema-less'' binary interchange formats.
Many sources compare data serialization formats and show Protocol
Buffers very favorably to the alternatives; see
\citet{Sumaray:2012:CDS:2184751.2184810} for one such comparison.

@@

But when the values are specified as character strings, RProtoBuf
will automatically coerce them into a true 64-bit integer types 
before storing them in the Protocol Buffer message:

@@

There are \Sexpr{n} standard data sets included in the base-r \pkg{datasets}
package. These datasets include data frames, matrices, time series, tables lists,
and some more exotic data classes. The \texttt{can\_serialize\_pb} method can be 
used to determine which of those can fully be converted to the \textt{rexp.proto}
Protocol Buffer representation:
